---
title: "Model_Supplement"
author: "Ana Miller-ter Kuile"
date: "6/26/2020"
output:
  word_document: default
  html_document: 
      theme: readable
      df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


```{r, include = FALSE}
library(here) #tidy data
library(tidyverse) #tidy data
library(ggplot2) #visualize data
library(effects) #dotplots and allEffects plots
library(DHARMa) #model diagnostics
library(MuMIn) #model diagnostics
library(glmmTMB) #mixed models
library(performance) #for binomial model fit binned residuals
library(cowplot) #plot grid at end
library(vegan) #adonis
library(esc) #effect sizes

```

# Diet Measure Models {.tabset}

## 1. Prey Detection

### A. Mesocosm

```{r, include = FALSE}
source(here("code",
            "4_analyses_figures",
            "4a_prey_detection.R"), local = knitr::knit_global())
```

For mesocosm consumers, the full model is of the form:

**presence ~ Sterilized, family = binomial**

where **presence** is the binary 0-1 detection of the offered prey item (*Oxya japonica*) in the sample and **Sterilized** is a two-level factor of either *surface sterilized* or *not surface sterilized*.  

and the null model is:

**presence ~ 1, family = binomial**

####Model comparison with AICc

```{r}
AICc(lab_detect_mod, lab_null_model)
```

#### Model summary

p-value of the surface sterilization fixed effect as marginally significant:

```{r}
summary(lab_detect_mod)
```

#### Marginal means graph

A marginal means graph shows a decreased in detection with surface steriliation: 

```{r}
plot(allEffects(lab_detect_mod))
```

#### Model diagnostics

```{r}
simulationOutput_lab <- simulateResiduals(fittedModel = lab_detect_mod) 
fit_lab <- plot(simulationOutput_lab, asFactor=TRUE)
binned_residuals(lab_detect_mod)
```

### B. Natural

For natural consumers, the full model is of the form:

**presence ~ Sterilized, family = binomial**

where **presence** is the binary 0-1 detection of any potential prey in the sample and **Sterilized** is a two-level factor of either *surface sterilized* or *not surface sterilized*.  

and the null model is:

**presence ~ 1, family = binomial**

#### Model comparison with AICc

```{r}
AICc(fld_detect_mod, fld_null_model)
```

#### Model summary

The sterilized term is non-significant:

```{r}
summary(fld_detect_mod)
summary(fld_null_model)
```

#### Model diagnostics

```{r}
simulationOutput_fld <- simulateResiduals(fittedModel = fld_null_model) 
fit_fld <- plot(simulationOutput_fld, asFactor=TRUE)
binned_residuals(fld_null_model)
```

### C. Summary

```{r, echo = FALSE}
plot_grid(a, c, nrow= 2, align = "hv")
```

## 2. Prey DNA Abundance

```{r, include = FALSE}
source(here("code",
            "4_analyses_figures",
            "4b_abundance_analyses.R"), 
       local = knitr::knit_global())
```

### A. Mesocosm

For mesocosm consumers, the full model is of the form:

**offered prey ~ Sterilized, offset = log(total), family = "genpois")**

where **offered prey** is the abundance of DNA from the offered prey item (*Oxya japonica*) in the sample, **Sterilized** is a two-level factor of either *surface sterilized* or *not surface sterilized*, and the offset term of **total** offset transforms the abundance value by the total DNA read abundance in the sample, since there is a huge spread in the raw DNA abundances.  

and the null model is:

**offered prey ~ 1, offset = log(total), family = "genpois")**

#### Model comparison with AICc

```{r, include = FALSE}
lab_mod <- glmmTMB(known ~ Sterilized,
                   data = lab_all_nz,
                   offset = log(total),
                   REML = FALSE,
                   family = "genpois")

lab_null <- glmmTMB(known ~ 1,
                   data = lab_all_nz,
                   offset = log(total),
                   REML = FALSE,
                   family = "genpois")
```

```{r}
AICc(lab_mod, lab_null)
```

#### Model summary

```{r, include = FALSE}
lab_mod <- glmmTMB(known ~ Sterilized,
                   data = lab_all_nz,
                   offset = log(total),
                   family = "genpois")

lab_null <- glmmTMB(known ~ 1,
                    data = lab_all_nz,
                    offset = log(total),
                    family = "genpois")
```

```{r}
summary(lab_mod)
summary(lab_null)
```

#### Model diagnostics

```{r}
plot(residuals(lab_null))
simulationOutput <- simulateResiduals(fittedModel = lab_null) 
fit <- plot(simulationOutput, asFactor=TRUE)
zi <- testZeroInflation(simulationOutput) 
od <- testDispersion(simulationOutput)
```

### B. Natural

For natural consumers, the full model is of the form:

**prey ~ Sterilized, offset = log(total), family = "genpois")**

where **prey** is the abundance of potential prey DNA in the sample, **Sterilized** is a two-level factor of either *surface sterilized* or *not surface sterilized*, and the offset term of **total** offset transforms the abundance value by the total DNA read abundance in the sample, since there is a huge spread in the raw DNA abundances.  

and the null model is:

**offered prey ~ 1, offset = log(total), family = "genpois")**

#### Model comparison with AICc

```{r, include = FALSE}
fld_mod <- glmmTMB(prey ~ Sterilized,
                   data = fld_all_nz,
                   offset = log(total),
                   REML = FALSE,
                   family = "genpois")

fld_null <- glmmTMB(prey ~ 1,
                   data = fld_all_nz,
                   offset = log(total),
                   REML = FALSE,
                   family = "genpois")
```

```{r}
AIC(fld_mod, fld_null)
```

#### Model summary

```{r, include = FALSE}
fld_mod <- glmmTMB(prey ~ Sterilized,
                   data = fld_all_nz,
                   offset = log(total),
                   family = "genpois")

fld_null <- glmmTMB(prey ~ 1,
                    data = fld_all_nz,
                    offset = log(total),
                    family = "genpois")
```

```{r}
summary(fld_mod)
summary(fld_null)
```
#### Model diagnostics

```{r}
plot(residuals(fld_null))
simulationOutput <- simulateResiduals(fittedModel = fld_null) 
fit <- plot(simulationOutput, asFactor=TRUE)
zi <- testZeroInflation(simulationOutput) 
od <- testDispersion(simulationOutput)
```

### C. Summary

```{r, echo = FALSE}
plot_grid(b_2, e_2, nrow = 2, align = "vh")
```

## 3. Natural: Prey DNA Richness and Composition

```{r, include = FALSE}
source(here("code",
            "4_analyses_figures",
            "4d_field_richness.R"), local = knitr::knit_global())

source(here("code",
            "4_analyses_figures",
            "4c_field_composition.R"), local = knitr::knit_global())
```

### A. Richness 

We looked at richness of diet within each natural predator diet, with richness being the richness of family-level taxonomic assignments in each sample. The full model for richness is:

**SR ~ Sterilized, family = poisson**

where **SR** is taxonomic richness in a sample (concatenated at the family level) and **Sterilized** is a two-level factor of either *surface sterilized* or *not surface sterilized*.

and the null model is:

**SR ~ Sterilized, family = poisson**

#### Model comparison with AICc

```{r, include = FALSE}
#create a model with and without surface sterilization effect, with poisson
#distribution since these are species count data
#set REML to false so that we can do AICc comparision
rich_mod <- glmmTMB(SR ~ Sterilized,
                    data = richness, 
                    family = poisson,
                    REML = FALSE)

rich_null <- glmmTMB(SR ~ 1,
                    data = richness, 
                    family = poisson, 
                    REML = FALSE)

#compare them with AIC, showing that the null is a better fit
```


```{r}
AICc(rich_mod, rich_null)
```

#### Model summary

```{r, include = FALSE}
#re-fit with REML
rich_null <- glmmTMB(SR ~ 1,
                     data = richness, 
                     family = poisson)

rich_mod <- glmmTMB(SR ~ Sterilized,
                    data = richness, 
                    family = poisson)
```


```{r}
#based on this summary, surface sterilizatoin treatment is 
#non-significant. 
summary(rich_mod)
summary(rich_null)
```
#### Model diagnostics 

```{r}
plot(residuals(rich_null))
simulationOutput <- simulateResiduals(fittedModel = rich_null) 
fit <- plot(simulationOutput, asFactor=TRUE)
zi <- testZeroInflation(simulationOutput) 
od <- testDispersion(simulationOutput) 
```

### B. Composition

We looked at presence-absence taxonomic composition of prey DNA using a GLMM-based PERMANOVA approach. Specifically, this GLMM is run by saying, how does the fixed effect of sterilization impact presence, with a random effects structure with both a random interept term for Family_ncbi (let each family have a different intercept) and a random slopes term for surface sterilization treatment (let each family's relationship with with surface sterilization differ, ie let some families increase with surface sterilization, and others decrease)

The full model looks like:

**presence ~ Sterilized + (1+Sterilized|Family_ncbi), family = "binomial"**

And the null looks like:

**presence ~ 1 + (1|Family_ncbi), family = "binomial"**

#### Model comparison with AICc

```{r}
AICc(comp_mod, comp_null)
```

#### Model summary

```{r}
summary(comp_null)
summary(comp_mod) #sterilization term not significant
```

#### Model diagnostics 

```{r}
binned_residuals(comp_null)
simulationOutput <- simulateResiduals(fittedModel = comp_null)
fit <- plot(simulationOutput, asFactor=TRUE)
```

#### Supplementary: Compare to adonis()

The results are similar with an adonis() call from vegan, with the structure:

**comp1 ~ Sterilized, data = meta_field, dist = "jaccard", binary = TRUE**

Where **comp1** is a matrix of interactions by individual, **Sterilized** is a binary fixed effect. We selected the Jaccard dissimilarlity index (indicating that data are presence-absence with binary=TRUE) since the Jaccard dissimilarity index is functionally Bray-Curtis dissimilarity, but better suited for presence-absence data

```{r}
adonis(comp1 ~ Sterilized, data = meta_field, dist = "jaccard", binary = TRUE)
```

### C. Summary

```{r, echo = FALSE}
rich_graph
```

```{r, out.width = "100%", echo = FALSE}
heat_map_family
```

